OA Share

### 2020-12-17 analysis/008_subject_exploration.Rmd
re order, first overall volume, then closer look into licenses

```{r}
hybrid_subject_19 <- hybrid_subject %>% 
  mutate(prop = oa /articles) %>%
  filter(issued_year == "2019", !is.na(percentile)
         #, prop > 0.01 & prop < 0.15) 
         )%>%
  distinct(issn, prop, percentile, snip, sjr)
```

@@

```{r}
cor.test(hybrid_subject_19$prop, hybrid_subject_19$snip, method = "spearman")
```

plot
```{r}
ggplot(hybrid_subject_19, aes(prop, snip)) + geom_point(alpha = .3) + geom_smooth(method = "lm") +
  coord_cartesian(xlim = c(0., 0.7), ylim = c(0.5, 6)) +
  labs(x = "OA Uptake Rate", y = "SNIP") +
  theme_cowplot()
```

@@

```{r}
hybrid_volume_jn <- hybrid_volume %>%
  group_by(issn) %>%
  summarise(n_oa = n_distinct(doi))

share_per_invoicing_type <- hybrid_volume %>%
  group_by(oa_sponsor_type, issn) %>%
  summarise(n_oa_type = n_distinct(doi)) %>%
  left_join(hybrid_volume_jn, by = "issn") %>%
  mutate(prop = n_oa_type / n_oa) %>%
  left_join(jn_subjects, by = "issn") %>%
  ungroup()
share_per_invoicing_type %>%
  filter(oa_sponsor_type == c("FundingBody")) %>%
  ggplot(aes(fct_reorder(top_level, prop, .fun = median, .desc = TRUE), prop)) +
  geom_boxplot() +
  coord_flip()
```

>>>>

```{r}
hybrid_subject_19 <- hybrid_subject %>% 
  mutate(prop = oa /articles) %>%
  filter(issued_year == "2019", !is.na(percentile)
         , prop != 0) %>%
  distinct(issn, prop, percentile, snip, sjr)
```

@@

```{r}
cor.test(hybrid_subject_19$prop, hybrid_subject_19$percentile, method = "spearman")
```

plot
```{r}
ggplot(hybrid_subject_19, aes(prop, snip)) + geom_point(alpha = 0.2) + 
  geom_smooth(method = "loess", se = TRUE) +
 # coord_cartesian(xlim = c(0., 0.7), ylim = c(0.5, 6)) +
  labs(x = "OA Uptake Rate", y = "SNIP") +
  theme_cowplot()
```

@@

```{r}
# hybrid_volume_jn <- hybrid_volume %>%
#   group_by(issn) %>%
#   summarise(n_oa = n_distinct(doi))
# 
# share_per_invoicing_type <- hybrid_volume %>%
#   group_by(oa_sponsor_type, issn) %>%
#   summarise(n_oa_type = n_distinct(doi)) %>%
#   left_join(hybrid_volume_jn, by = "issn") %>%
#   mutate(prop = n_oa_type / n_oa) %>%
#   left_join(jn_subjects, by = "issn") %>%
#   ungroup()
# share_per_invoicing_type %>%
#   filter(oa_sponsor_type == c("FundingBody")) %>%
#   ggplot(aes(fct_reorder(top_level, prop, .fun = median, .desc = TRUE), prop)) +
#   geom_boxplot() +
#   coord_flip()
```
